Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-15 intro.tex
clean up earlier todos

\begin{itemize}
\item We develop these ideas in the form of a logic for working with virtual-address-space-relative assertions,
      implemented as an embedded separation logic within Iris~\cite{jung2018iris} separation logic.
\item We prove the soundness of our \textsf{vProp} logic with respect to a RISC-like fragment of \textsf{AMD64} instructions.
\item We verify simplified versions of several critical virtual-memory-related pieces of OS functionality, 
      including mapping  pages, the assembly code for switching address spaces, and code which manipulates page
      tables for \emph{currently mapped memory} without disturbing mappings.\todo[inline]{Colin says: I have optimistically
      added this last example to the text here, because I think we can probably do it. Leave this TODO
      here until we either do or cut it.}
      The latter in particular goes beyond the capabilities of prior work.
\end{itemize}

>>>>

\begin{itemize}
\item We develop these ideas in the form of a logic for working with virtual-address-space-relative assertions,
      implemented as an embedded separation logic within Iris~\cite{jung2018iris} separation logic.
\item We prove the soundness of our \textsf{vProp} logic with respect to a RISC-like fragment of \textsf{AMD64} instructions.
\item We verify simplified versions of several critical virtual-memory-related pieces of OS functionality, 
      including mapping  pages, and the assembly code for switching address spaces. 
      The latter in particular goes beyond the capabilities of prior work, and reveals unexpected
	subtleties.
\end{itemize}
